\begin{center}
\textbf{THE ABSTRACT}
\end{center}
\vspace{4pt}

127 pages, 6 pictures

\noindent ASSET EXCHANGE, DISTRIBUTED LEDGERS, BLOCKCHAIN, TRUST,\\
INTEROPERABILITY, ATOMIC SWAP, HTLC, ETHEREUM, BITSHARES, REACT.

\vspace{4pt}

Topic of the graduation thesis: "Development of a service for asset exchange between isolated distributed ledgers without establishing trust."

As part of the work, research was conducted on distributed ledger technology (DLT), including blockchain technology, and various mechanisms for solving the interoperability problem of blockchains in terms of asset exchange between different blockchain networks were studied.

Thesis results:
\begin{enumerate}
\item Existing methods of asset exchange were studied and their limitations in the context of security and the need for trust between parties were identified.
\item A prototype service was created for asset exchange between blockchains.
\item Modular and system testing was conducted, confirming the operability and security of the developed service.
\end{enumerate}

The developed service and analysis results can be used in financial organizations involved in international settlements and needing alternative settlement mechanisms ori n projects related to decentralized finance (DeFi) to ensure more predictable mechanisms when conducting transactions.

The developed service demonstrated high efficiency and security in asset exchange between isolated distributed ledgers. This makes the proposed approach promising for widespread use in various fields related to blockchain technologies and decentralized finance.

\newpage